COG-ED Manuscript

### 2021-10-14 06_Paper/COG-ED/Manuscript.Rmd
implemented annotations in methods section and changed data frame of RT data

  # the target column will contain 1 for targets and 0 for all non-targets
  data_nback[data_nback == "Target"] <- 1
  data_nback[data_nback == "Pretarget"|data_nback == "Lure"|data_nback == "Distractor"] <- 0
  data_nback$target <- as.numeric(data_nback$target)
  # the response column will contain 1 for responses and 0 for all non-responses
  data_nback[data_nback == "left"|data_nback == "right"] <- 1
  data_nback[data_nback == "None"] <- 0
  data_nback$response <- as.numeric(data_nback$response)

  # exclude trials after incorrect responses

  data_nback <- data_nback[-c(which(data_nback$correct == 1) + 1), ]

  # exclude trials with reaction times below 200 ms

  data_nback <- data_nback[-c(which(data_nback$rt < 0.2)), ]

@@

We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
# FIXME add version no. and packages
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/CERED.

## Questionnaires
To assess perceived task load, we used the NASA Task Load Index (NTLX) [@Hart1988], a 6-item questionnaire with the dimensions mental load, physical load, effort, frustration, performance, and time pressure.
FIXME: NTLX seems not to be the commonly used abbreviation. We my refer to NASA TLX / NASA-TLX or just TLX. We may provide more information (see Strobel et al. 2020):
In the NASA-TLX, participants evaluate their subjective perception of the mental, physical and temporal svs of a particular task, as well as their performance, effort and frustration during the task on a 20-point scale for each dimension. In its original, the NASA-TLX also requires comparisons of two dimensions each. For this study, we relinquished the comparison due to time restrictions.

Need for Cognition was assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
FIXME: We may need to add information on example items, rating scale and reliability (see diffpp):
_Need for Cognition_ was assessed with the 16-item short version of the German NFC scale [@Bless1994]. Responses to each item (e.g., "Thinking is not my idea of fun", recoded) were recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree). The scale shows comparably high internal consistency [Cronbach’s $\alpha$ > .80; @Bless1994; @Fleischhauer2010].

Several other personality questionnaires were used in this study but are the topic of the registered report for the second lab session regarding ED in emotion regulation tasks and will not be analyzed here.
A full list of questionnaires and measures can be found in Appendix 1.

## Procedure
Participants for the pilot study were recruited using the software *ORSEE* [@Greiner2015].
The final sample consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
Each participant completed two sessions in the lab one week apart, and a battery of personality questionnaires at least two days after the second session.
In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
The paradigm started with the n-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
The levels were referred to by colour (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
After each level, participants filled out the NTLX on a tablet to provide a state measure of cognitive effort.
Then, they completed the ED procedure on screen, where each possible pairing of the four n-back levels was presented in a randomized order.
Participants were instructed to decide as realistically as possible, because one of their choices from the last iteration steps would be randomly chosen for one final run of n-back.
The level and its monetary value were presented on screen and participants completed one run, but this was only to incentivise truthful behaviour in the ED procedure, so the n-back data of this part was not analyzed.
The second session consisted of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
The paradigm followed the same structure of task, ED procedure, and repetition of a random "level" as in session one. <!--CS: Achtung: das wurde verändert: Sie wiederhuolen nicht random ein Level sondern können sich nochmal frei entscheiden! -->
There were many more measures and hypotheses regarding session two, which will be the topic of a different registered report.
Two days after the second session, participants received a link to the NFC scale and other personality questionnaires to provide a trait measure of preference for cognitive effort.
Participants received 8€ per hour or course credit for participation, plus payment for the randomly chosen level.
Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].

## Analysis
We conducted all analysis as described in Westbrook et al. [-@Westbrook2013].
The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
Declining performance was investigated by calculating an analysis of variance (ANOVA) with three linear contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another ANOVA with three linear contrasts was computed to compare the mean reaction time (RT) between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NTLX ratings, six ANOVAs were computed, one for each NTLX subscale, and each with six linear contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
The SVs were calculated by adding or subtracting the final iteration value of 0.015625 from the monetary value of the flexible level for each ED round, depending on the participant's choice in the last iteration.
Then, the final monetary values were divided by 2€, and the SV of each level per participant was computed by averaging all final monetary values of each level, regardless of whether it was fixed or flexible.
An ANOVA with six linear contrasts was computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Each ANOVA in the analysis was followed up by a Tukey's test.
# would it be possible to compare the originally calculated SV with our new one?
To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
**MLM explanation goes here**
The association of ED and NFC was done using three separate regressions.
One regression used the AUC of each participant's SVs to predict their NFC score.
The second regression additionally included the mean of the NTLX subscales' AUCs of each participant as a predictor.
And the last regression used the AUC of each participant's SV, the AUC of the NTLX mental load subscale, and the AUC of the NTLX effort subscale to predict each participant's NFC score.

>>>>

  # the target column will contain 1 for targets and 0 for all non-targets

  data_nback[data_nback == "Target"] <- 1
  data_nback[data_nback == "Pretarget"|data_nback == "Lure"|data_nback == "Distractor"] <- 0
  data_nback$target <- as.numeric(data_nback$target)

  # the response column will contain 1 for responses and 0 for all non-responses

  data_nback[data_nback == "left"|data_nback == "right"] <- 1
  data_nback[data_nback == "None"] <- 0
  data_nback$response <- as.numeric(data_nback$response)

  # create a new data frame for the data that is being used for reaction time analysis
  # (we cannot exclude trials from the main data frame because the computation of d prime depends on hit-ratios, not reaction time)

  # exclude trials after incorrect responses and with reaction times below 200 ms

  data_RT <- data_nback[-c(which(data_nback$correct == 1) + 1), ]
  data_RT <- data_RT[-c(which(data_RT$rt < 0.2)), ]

@@

We used *R Studio* [@RCT2020; @RStudioTeam2020] with the main packages *tidyverse* [@Wickham2019] and *basetestR* [@Makowski2019] for all our analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/CERED.

## Questionnaires
To assess perceived task load, we used the 6-item NASA Task Load Index (NASA-TLX) [@Hart1988].
In the NASA-TLX, participants evaluate their subjective perception of mental load, physical load, effort, frustration, performance, and time pressure during the task on a 20-point scale.
Need for Cognition was assessed using the 16-item short form of the Need for Cognition Scale [@Bless1994; @Cacioppo1984].
Responses to each item (e.g., "Thinking is not my idea of fun", recoded) were recorded on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
The scale shows comparably high internal consistency [Cronbach’s $\alpha$ > .80; @Bless1994; @Fleischhauer2010].
Several other personality questionnaires were used in this study but are the topic of the registered report for the second lab session regarding ED in emotion regulation tasks and will not be analyzed here.
A full list of questionnaires and measures can be found in Appendix 1.

## Procedure
Participants for the pilot study were recruited using the software *ORSEE* [@Greiner2015].
The final sample consisted of $N=$ `r length(datalist_ED)` participants (`r round((table(data_quest$gender)[2]/length(datalist_ED))*100, digits = 1)`% female, $M=$`r round(mean(data_quest$age, na.rm = TRUE), digits = 1)`($SD=$`r round(sd(data_quest$age, na.rm = TRUE), digits = 1)`) years old).
Each participant completed two sessions in the lab one week apart, and a battery of personality questionnaires at least two days after the second session.
In the first session, participants provided informed consent and demographic data before completing the computer-based paradigm.
The paradigm started with the n-back levels one to four, presented sequentially with two runs per level, consisting of 64 consonants (16 targets, 48 non-targets) per run.
The levels were referred to by colour (1-back black, 2-back red, 3-back blue, 4-back green) to avoid anchor effects in the ED procedure.
After each level, participants filled out the NTLX on a tablet to provide a state measure of cognitive effort.
Then, they completed the ED procedure on screen, where each possible pairing of the four n-back levels was presented in a randomized order.
Participants were instructed to decide as realistically as possible, because one of their choices from the last iteration steps would be randomly chosen for one final run of n-back.
The level and its monetary value were presented on screen and participants completed one run, but this was only to incentivise truthful behaviour in the ED procedure, so the n-back data of this part was not analyzed.
The second session consisted of an emotion regulation task with negative pictures and the instruction to suppress facial reactions, detach cognitively from the picture content, and distract oneself, respectively.
The paradigm followed the same structure of task and ED procedure, but the emotion regulation strategy at the end was not randomly chosen, instaed participants could decide which strategy they wanted to use again.
There were many more measures and hypotheses regarding session two, which will be the topic of a different registered report.
Two days after the second session, participants received a link to the NFC scale and other personality questionnaires to provide a trait measure of preference for cognitive effort.
Participants received 30€ in total or course credit for participation.
Study data were collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].

## Analysis
We aimed to conduct all analysis as described in Westbrook et al. [-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations in terms of data cleaning and degrees of freedom in the statistical procedures.
The performance measure *d'* was computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate [@Macmillan1990].
Declining performance was investigated by calculating an analysis of variance (ANOVA) with three linear contrasts comparing *d'* between two levels of 2-, 3-, and 4-back at a time.
Another ANOVA with three linear contrasts was computed to compare the mean reaction time (RT) between two levels of 2-, 3-, and 4-back at a time.
To investigate changes in NTLX ratings, six ANOVAs were computed, one for each NTLX subscale, and each with six linear contrasts comparing the ratings between two levels of 1-, 2-, 3-, and 4-back at a time.
The SVs were calculated by adding or subtracting the final iteration value of 0.015625 from the monetary value of the flexible level for each ED round, depending on the participant's choice in the last iteration.
Then, the final monetary values were divided by 2€, and the SV of each level per participant was computed by averaging all final monetary values of each level, regardless of whether it was fixed or flexible.
An ANOVA with six linear contrasts was computed, comparing the SVs between two levels of 1-, 2-, 3-, and 4-back at a time.
Each ANOVA in the analysis was followed up by a Tukey's test.
# would it be possible to compare the originally calculated SV with our new one?
To determine the influence of task performance in the association of SVs and n-back level, we set up a multi-level model.
**MLM explanation goes here**
The association of ED and NFC was done using three separate regressions.
One regression used the AUC of each participant's SVs to predict their NFC score.
The second regression additionally included the mean of the NTLX subscales' AUCs of each participant as a predictor.
And the last regression used the AUC of each participant's SV, the AUC of the NTLX mental load subscale, and the AUC of the NTLX effort subscale to predict each participant's NFC score.
